%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%-------------------------------------------------------------------------------
  \cventry
    {Engineer} % Job title
    {MediaTek Inc.} % Organization
    {Taipei City, Taiwan} % Location
    {August 2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {2015 \href{https://mcs.mediatek.com}{\textbf{MCS (MediaTek Cloud Sandbox)}}: Develop a cloud based data service platform for IoT devices. Keyword: Node.js, Angular 1, SPA, React, Stylus, Websocket, Google Map, i18n.}
        \item {2017 \href{https://mcslite.netlify.com/}{\textbf{MCS Lite}}: Desktop app version of MCS which can be quickly built and get started with. Keyword: React, Redux, Cycle.js, Rxjs, OSS, NW.js, i18n.}
        \item {2018 \href{https://medium.com/mediatekcloudsandbox/\%E5\%A6\%82\%E4\%BD\%95\%E9\%80\%8F\%E9\%81\%8E-scene-\%E5\%A0\%B4\%E6\%99\%AF-\%E5\%8A\%9F\%E8\%83\%BD\%E5\%BF\%AB\%E9\%80\%9F\%E6\%89\%93\%E9\%80\%A0\%E7\%89\%A9\%E8\%81\%AF\%E7\%B6\%B2\%E6\%87\%89\%E7\%94\%A8-1-d10d0d687742}{\textbf{MCS Scenes}}: Implemented a drag and drop web service to monitor IoT data channels in a scene. Keyword: GraphQL, Apollo, Next.js, Proxy, i18n, Docker.}
        \item {2018 \textbf{MCS Enterprise}: Enterprise version of MCS. Keyword: Docker, Kubernetes.}
        \item {2016 \href{https://labs.mediatek.com}{\textbf{MediaTek Labs}}: Develop an IoT developer program that provides all the tools and resources. Keyword: Laravel, React, i18n, PWA.}
        \item {2015 \href{https://mcs.mediatek.com/resources/latest/introduction}{\textbf{MCS Resources}}:A static web service for MCS documents. Built an automatic CI/CD workflow that transform markdown into HTML content. Keyword: Bamboo, CI/CD, S3, React, Stylus, i18n.}
        \item {2016 \href{https://medium.com/mediatekcloudsandbox/\%E5\%B0\%87\%E6\%82\%A8\%E7\%9A\%84\%E8\%A3\%9D\%E7\%BD\%AE\%E8\%A8\%AD\%E7\%82\%BA\%E5\%85\%AC\%E9\%96\%8B\%E4\%B8\%A6\%E5\%88\%86\%E4\%BA\%AB\%E7\%B5\%A6\%E4\%BB\%BB\%E4\%BD\%95\%E4\%BA\%BA\%E7\%80\%8F\%E8\%A6\%BD-a96d47ba5859}{\textbf{MCS Public}}: A web service that you can share your own IoT device to everyone. Keyword: React, Redux, SSR, Websocket.}
        \item {2016 \textbf{MCS Analysis}: Built an internal data visualization service. Keyword: React, Redux, SVG.}
      \end{cvitems}
    }

%-------------------------------------------------------------------------------
  \cventry
    {Summer Internship} % Job title
    {MediaTek Inc.} % Organization
    {Hsinchu City, Taiwan} % Location
    {July 2014 - August 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {MCS (MediaTek Cloud Sandbox): Develop MCS 1.0. Keyword: Angular, Gulp, RESTful, Node.js.}
      \end{cvitems}
    }

%-------------------------------------------------------------------------------
  \cventry
    {Co-Founder} % Job title
    {雲鼎天秤} % Organization
    {Taipei City, Taiwan} % Location
    {October 2013 - December 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop a iOS app for user to share notes in real-time. Keyword: Node.js, Websocket, iOS.}
      \end{cvitems}
    }

%-------------------------------------------------------------------------------
  \cventry
    {Front-End Summer Internship} % Job title
    {\href{https://whoscall.com}{Gogolook Whoscall}} % Organization
    {Taipei City, Taiwan} % Location
    {July 2013 - December 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web Designer \& Developer \& Data Processor}
        \item {Develop a web service for customer to enable their account via point card. Keyword: jQuery.}
        \end{cvitems}
    }

%-------------------------------------------------------------------------------
  \cventry
    {Venture Capital Summer Internship} % Job title
    {\href{http://tmi.vc}{TMI 台灣創意工場}} % Organization
    {Taipei City, Taiwan} % Location
    {July 2012 - December 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Startup Survey \& Web development}
        \item {Assist startups to develop POC features. Keyword: Ruby, ROR, JavaScript.}
      \end{cvitems}
    }

%-------------------------------------------------------------------------------
\end{cventries}
