%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	Services
%-------------------------------------------------------------------------------
\cvsubsection{Services}
\begin{cvhonors}

%-------------------------------------------------------------------------------
  \cvhonor
    {\textbf{Project master data management platform}: \textmd{A Master Data management platform to analysis project stage in MediaTek. Keyword: Next.js, GraphQL, Apollo, typescript, react hooks, GraphQL Code gen, material-ui}} % Award
    {MediaTek} % Event
    {Front-End Lead} % Location
    {2020} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\textbf{Debugger platform}: \textmd{A web UI to analysis the status of jobs and integrate dataflow with Splunk software in MediaTek. Keyword: Next.js, GraphQL, Apollo, typescript, react hooks, GraphQL Code gen, material-ui, Splunk}} % Award
    {MediaTek} % Event
    {Front-End Lead} % Location
    {2020} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\textbf{Data analysis story showcase}: \textmd{An AI show case page in MediaTek. Keyword: Gatsby, GraphQL, styled-components, typescript, react hooks, GraphQL Code gen}} % Award
    {MediaTek} % Event
    {Front-End Lead} % Location
    {2019} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://neuropilot.mediatek.com/}{NeuroPilot Simulator}: \textmd{An AI Simulator provides pre-silicon functionality and performance hint for early-stage AI development with NeuroPilot. Keyword: Next.js, GraphQL, Apollo, Flow type, docker, pkg}} % Award
    {MediaTek} % Event
    {Front-End Lead} % Location
    {2019} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://neuropilot.mediatek.com/}{NeuroPilot Online Document}: \textmd{A MediaTek Ecosystem for AI Development. Keyword: Next.js, GraphQL, Apollo, Flow type}} % Award
    {MediaTek} % Event
    {Front-End Lead} % Location
    {2019} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\textbf{Decoder tool website}: \textmd{Develop a decoder tool web UI for RD to analysis encoded files in MediaTek. Keyword: Next.js, GraphQL, Apollo, Flow type}} % Award
    {MediaTek} % Event
    {Front-End Lead} % Location
    {2019} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\textbf{MediaTek Cloud Sandbox Enterprise}: \textmd{Enterprise version of MCS. Keyword: Docker, Kubernetes.}} % Award
    {MediaTek} % Event
    {Front-End Owner} % Location
    {2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://medium.com/mediatekcloudsandbox/\%E5\%A6\%82\%E4\%BD\%95\%E9\%80\%8F\%E9\%81\%8E-scene-\%E5\%A0\%B4\%E6\%99\%AF-\%E5\%8A\%9F\%E8\%83\%BD\%E5\%BF\%AB\%E9\%80\%9F\%E6\%89\%93\%E9\%80\%A0\%E7\%89\%A9\%E8\%81\%AF\%E7\%B6\%B2\%E6\%87\%89\%E7\%94\%A8-1-d10d0d687742}{MediaTek Cloud Sandbox Scenes}: \textmd{A drag and drop web service to monitor IoT data channels in a scene. Keyword: GraphQL, Apollo, Next.js, Proxy, i18n, Docker.}} % Award
    {MediaTek} % Event
    {Front-End Lead} % Location
    {2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://mcslite.netlify.com/}{MediaTek Cloud Sandbox Lite}: \textmd{Desktop app version of MediaTek Cloud Sandbox which can be quickly built and get started with. Keyword: React, Redux, Cycle.js, RxJS, OSS, NW.js, i18n.}} % Award
    {MediaTek} % Event
    {Front-End} % Location
    {2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\textbf{MediaTek Cloud Sandbox Analysis}: \textmd{An internal data visualization service. Keyword: React, Redux, SVG.}} % Award
    {MediaTek} % Event
    {Front-End} % Location
    {2016} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://medium.com/mediatekcloudsandbox/\%E5\%B0\%87\%E6\%82\%A8\%E7\%9A\%84\%E8\%A3\%9D\%E7\%BD\%AE\%E8\%A8\%AD\%E7\%82\%BA\%E5\%85\%AC\%E9\%96\%8B\%E4\%B8\%A6\%E5\%88\%86\%E4\%BA\%AB\%E7\%B5\%A6\%E4\%BB\%BB\%E4\%BD\%95\%E4\%BA\%BA\%E7\%80\%8F\%E8\%A6\%BD-a96d47ba5859}{MediaTek Cloud Sandbox Public}: \textmd{A web service that you can share your own IoT device to everyone. Keyword: React, Redux, SSR, WebSocket.}} % Award
    {MediaTek} % Event
    {Front-End} % Location
    {2016} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://mcs.mediatek.com/}{MediaTek Cloud Sandbox}: \textmd{A cloud based data service platform for IoT devices. Keyword: Node.js, Angular 1, SPA, React, Stylus, WebSocket, Google Map, i18n.}} % Award
    {MediaTek} % Event
    {Front-End} % Location
    {2015} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://mcs.mediatek.com/resources/latest/introduction}{MediaTek Cloud Sandbox Resources}: \textmd{A static web service for MediaTek Cloud Sandbox documents. Built an automatic CI/CD workflow that transform markdown into HTML content. Keyword: Bamboo, CI/CD, S3, React, Stylus, i18n.}} % Award
    {MediaTek} % Event
    {Front-End} % Location
    {2015} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://labs.mediatek.com/}{MediaTek Labs}: \textmd{An IoT developer program that provides all the tools and resources to make your IoT and wearable idea a reality. Keyword: Laravel, React, i18n, PWA.}} % Award
    {MediaTek} % Event
    {Front-End Owner} % Location
    {2016} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\textbf{MediaTek Cloud Sandbox}: \textmd{MediaTek Cloud Sandbox 1.0. Keyword: Angular, Gulp, RESTful, Node.js.}} % Award
    {MediaTek} % Event
    {Front-End} % Location
    {2014} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://kdchang.cc/Dr.Find}{Dr.Find}: \textmd{Visualize medical information in Taiwan}} % Award
    {IDEAS Tech hackathon by 財團法人資訊工業策進會} % Event
    {Front-End} % Location
    {Jul, 2014} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {Assignment Scoring System: \textmd{A project about scoring assignment online}} % Award
    {NTUIM} % Event
    {Fullstack} % Location
    {Jul, 2013} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{http://minna.herokuapp.com}{Mina}: \textmd{Real time note sharing}} % Award
    {HackNTU} % Event
    {Front-End} % Location
    {Jun, 2013} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{http://firebox.herokuapp.com}{Firebox}: \textmd{Play baseball in Firefox OS}} % Award
    {Firefox OS App Days} % Event
    {Front-End} % Location
    {May, 2013} % Date(s)


%-------------------------------------------------------------------------------
  \cvhonor
    {\href{http://emo-song.herokuapp.com}{EMO-SONG}: \textmd{Recommend music based on your emotion}} % Award
    {Web Retrieval and Mining} % Event
    {Data Mining} % Location
    {2013} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{http://yoho-taipei.herokuapp.com}{悠活臺北}: \textmd{A service which crawls the Yahoo horoscope and Taipei open data to integrate with Facebook API to recommend the suitable views in Taipei}} % Award
    {Yahoo! Open Hack Day} % Event
    {Front-End} % Location
    {Oct, 2012} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://sentiminer.herokuapp.com}{Sentiminer}: \textmd{Sentiment analysis}} % Award
    {NTU} % Event
    {Text Mining} % Location
    {2012} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{http://rumbleat.herokuapp.com/}{Rumbleat}: \textmd{What to eat today}} % Award
    {NTU Cloud Expo 台大資工雲端手機聯合期末展} % Event
    {Fullstack} % Location
    {2012} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {Ka.Sza: \textmd{A android app that you can upload your image to cloud for recognizing}} % Award
    {電信創新應用大賽} % Event
    {Android} % Location
    {2012} % Date(s)



%-------------------------------------------------------------------------------
\end{cvhonors}

%-------------------------------------------------------------------------------
%	Side Projects
%-------------------------------------------------------------------------------
\newpage
\cvsubsection{Side Projects}
\begin{cvhonors}

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/nextjs-tfjs-cnn}{nextjs-tfjs-cnn}: \textmd{Classifier using Keras VGG16 transfer learning with kaggle dataset.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Sep, 2019} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/imagemin-simple}{imagemin-simple}: \textmd{Replace images with minified one and generate small base64 image.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Dec, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/hsu-scripts}{hsu-scripts}: \textmd{CLI toolbox for common scripts for npm libraries.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Dec, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/remark-utils}{remark-utils}: \textmd{Reusable utils to build markdown service power by remarkjs and elasticlunr.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Nov, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/Mediatek-Cloud/mcs-ui}{mcs-ui}: \textmd{React components used by MCS.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Oct, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/acdlite/recompose}{recompose}: \textmd{A React utility belt for function components and higher-order components}} % Award
    {GitHub} % Event
    {Contributor} % Location
    {May, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-image-onload}{react-image-onload}: \textmd{React Image onLoad event.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Mar, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-overlay-pack}{react-overlay-pack}: \textmd{Reusable components to build Tooltip, Popover and Dialog.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Jan, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-input-files}{react-input-files}: \textmd{Reusable React input file component.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Jan, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-dnd-dropzone}{react-dnd-dropzone}: \textmd{Dropzone with render props built with react-dnd.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Jan, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-intl.macro}{react-intl.macro}: \textmd{Extract react-intl messages with babel-plugin-macros.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Jan, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/svgr.macro}{svgr.macro}: \textmd{Run svgr at build-time with babel-plugin-macros.}} % Award
    {GitHub} % Event
    {Owner} % Location
    {Jan, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/kentcdodds/babel-plugin-macros}{babel-plugin-macros}: \textmd{Enables zero-config, importable babel plugins}} % Award
    {GitHub} % Event
    {Contributor} % Location
    {Jan, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/graphql.macro}{graphql.macro}: \textmd{Compile GraphQL AST at build-time with babel-plugin-macros}}
    {GitHub} % Event
    {Owner} % Location
    {Jan, 2018} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-intl-cra}{react-intl-cra}: \textmd{Extract messages of Create React App from the command line}}
    {GitHub} % Event
    {Owner} % Location
    {Dec, 2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/todomvc-subscriptions}{todomvc-subscriptions}: \textmd{Fullstack TodoMVC with GraphQL subscriptions}}
    {GitHub} % Event
    {Owner} % Location
    {Dec, 2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/gh-polls-bot}{gh-polls-bot}: \textmd{A GitHub App built with Probot that automatically creates gh-polls in GitHub issues}}
    {GitHub} % Event
    {Owner} % Location
    {Nov, 2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/micro-website-api}{micro-website-api}: \textmd{An API microservice that crawls dynamic website powered by puppeteer}}
    {GitHub} % Event
    {Owner} % Location
    {Nov, 2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/micro-medium-api}{micro-medium-api}: \textmd{Microservice for fetching the latest posts of Medium with GraphQL}}
    {GitHub} % Event
    {Owner} % Location
    {Aug, 2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-progressive-bg-image}{react-progressive-bg-image}: \textmd{Medium style progressive background image for React based on Styled-components}}
    {GitHub} % Event
    {Owner} % Location
    {May, 2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/MCS-Lite/mcs-lite}{mcs-lite}: \textmd{An on-premises IoT cloud platform, which can be quickly built and get started with}}
    {GitHub} % Event
    {Owner} % Location
    {Jan, 2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/MCS-Lite/mcs-lite}{mcs-lite-ui}: \textmd{MediaTek Cloud Sandbox Lite Common UI and Websites}}
    {GitHub} % Event
    {Owner} % Location
    {Jan, 2017} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-grecaptcha}{react-grecaptcha}: \textmd{React.js Google reCAPTCHA v2 integration component}}
    {GitHub} % Event
    {Owner} % Location
    {May, 2016} % Date(s)

%-------------------------------------------------------------------------------
  \cvhonor
    {\href{https://github.com/evenchange4/react-intl-po}{react-intl-po}: \textmd{Extract POT from react-intl and convert back to json}}
    {GitHub} % Event
    {Owner} % Location
    {Mar, 2016} % Date(s)

%-------------------------------------------------------------------------------
\end{cvhonors}
